\documentclass{article}

\title{Lab 3}
\author{Keith Evan Schubert}

\begin{document}
\maketitle

\section{Objective}
The purpose of this lab is to implement a tiled dense matrix multiplication routine.

\section{Activity}

\begin{enumerate}
\item Login to kodiak.  cd to your mpplabs directory and type \verb1git pull1.
\item Edit the file \verb1<lab-directory>/main.cu1 to implement the following where indicated:
	\begin{enumerate}
	\item Allocate device memory
	\item Copy host memory to device
	\item Copy results from device to host
	\item Free device memory
	\end{enumerate}	 
\item Edit the file \verb1<lab-directory>/kernel.cu1 to initialize the thread block and kernel grid dimensions and invoke the CUDA kernel, and to implement the tiled matrix multiplication kernel code..
\item Compile and test your code.  
\begin{verbatim}
	cd <lab-directory>
	make
	nano sgemm-tiled.sh  # add sgemm-tiled commands per below
	    ~/<lab-directory>/sgemm-tiled			# Uses the default matrix sizes
	    ~/<lab-directory>/sgemm-tiled <m>			# Uses square m x m matrices
	    ~/<lab-directory>/sgemm-tiled <m> <k> <n>	# Uses (m x k) and 
	                                  # (k x n) input matrices
	qsub -q tardis sgemm-tiled.sh
\end{verbatim}
\end{enumerate}

\section{Turn in}
Upload to the course Canvas site:
\begin{enumerate}
\item a report that includes :
	\begin{enumerate}
	\item the output 
	\item analysis of the performance: Try the code for several sizes, square and non-square matrices, and matrices that fit and don't fit (neatly) in the blocks  How does the time change?  Does each part change the same?
	\item answer section where you answer the following:
		\begin{enumerate}
		\item In your kernel implementation, how many threads can be simultaneously scheduled for execution on a GeForce GTX 280 GPU, which contains 30 streaming multiprocessors? Use:
\begin{verbatim}
	nvcc --ptxas-options="-v" kernel.cu
\end{verbatim}
to see the resource usage of your kernel (although compilation will fail, it will only do so after compiling the kernel and displaying the relevant information). Show your work.
		\end{enumerate}
	\end{enumerate}
\item main.cu
\item kernel.cu
\end{enumerate} 
The cuda code will be graded for completeness, correctness, handling of boundary, and style (5pts).  The report will be graded on readability, clarity, analysis, and solution to the questions (5pts).


\section{Going Further}
There should be a definite improvement in time but the complexity should stay the same (how it grows relatively).  Think about at what point matrix multiply in this fashion becomes too long.  1 day? 1 week?  Estimate the problem size.  

\end{document}